The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
Explain MP dwarfs at low teff #7

In Section~\ref{sec:method} we assumed that any fibre- or time-dependent variations
in the \rave\ spectra are negligible.  This is provably incorrect. Indeed,
\citet{Kordopatis_2013} note that the effective resolution of \rave\
spectra varies from $6{,}500 < \mathcal{R} < 8{,}500$, and that the 
effective resolution is a function of time and position on the CCD (e.g., fibre number).  For this reason we ought to expect our derived stellar
parameters or abundances to be correlated with the fibre number, or over
time.  If significant, the trend could produce systematically offset
stellar abundances solely due to the fibre number.  We have not seen
evidence of these correlations in our results, however, we have only
performed cursory (non-exhaustive) experiments to investigate this issue.

@@

@@

>>>>

In Section~\ref{sec:method} we assumed that any fibre- or time-dependent variations
in the \rave\ spectra are negligible.  This is provably incorrect. Indeed,
\citet{Kordopatis_2013} note that the effective resolution of \rave\
spectra varies from $6{,}500 < \mathcal{R} < 8{,}500$, and that the 
effective resolution is a function of time and position on the CCD (e.g., fibre number).  For this reason we ought to expect our derived stellar
parameters or abundances to be correlated with the fibre number, or over
time.  If significant, the trend could produce systematically offset
stellar abundances solely due to the fibre number.  \citet{Kordopatis_2013}
conclude that resolution-based effects on the \rave\ stellar parameters
should be a second-order effect. We have not seen evidence of these 
resolution-based correlations in our results, however, we have only
performed cursory (non-exhaustive) experiments to investigate this issue.

@@

The fibre fringing is another example of how test spectra that are
unusual from the training set can be projected as peculiar artefacts in the
label space.  In other words, unusual spectra can appear as `clumps' in
regions of parameter space that we could consider as being normal 
(e.g., Solar-type stars).  We addressed this issue for the main-sequence
and giant models by using a joint model to calculate relative weights.
However, spectra that are unusual from the joint model training set can
still project as systematic artefacts.  An interrogation of our results
has identified one such group of metal-poor ($[{\rm Fe/H}] \approx -0.4$)
stars near $\teff \approx 3250$~K, which peculiarly sit above the isochrone. 
The \rave\ morphological classifications \citep{Matijevic_2012} indicate 
these stars have chromospheric emission, a feature not present in our 
training set.  Based on this (and other previously discussed) examples,
we recommend either a thorough investigation of unexpected structure
\footnote{Before submitting to \emph{Nature}} 
using all the available 
information from \rave, or judicious quality controls (e.g., requiring the 
morphological classification to be `normal') to remove these spurious measurements.

@@

\bibitem[Matijevi{\v c} et al.(2012)]{Matijevic_2012} Matijevi{\v c}, G., Zwitter, T., Bienaym{\'e}, O., et al.\ 2012, \apjs, 200, 14
